Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-11 paper/paper.tex
revisions after talking to igor about escli-host

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 250 0 0,clip,width=0.5\textwidth]{google-awards-workflow}  
  \caption{\label{fig:workflow}Infrastructure.}
\end{figure}

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

>>>>

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}  
  \caption{\label{fig:workflow}Infrastructure.}
\end{figure}

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.  The bug-finding process takes on input JS files from
regression test suites of various JS engines and generates warnings on
output. Boxes in the figure denote encapsulation; arrowed lines
indicate data flow. The cycle icons denote repetition--the leftmost
icon indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.
Considering the case where fuzzing is not selected, the oracle checks
whether or not the output produced for the input file is consistent
across all engine implementations. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. We used the open-source eshost-cli
project~\cite{eshost-cli} for that. Microsoft uses eshost-cli to check
functional discrepancies in the Chakra JS engine. Considering the case
where fuzzing~\cite{fuzz-testing-history} is selected, new inputs are
obtained from a given input using some off-the-shelf fuzzer. The
workflow with fuzzing is similar to the workflow without fuzzing. In
this case, however, the checker can produce multiple warnings for a
given input. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are
generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
